Recipient plant traits are important determinants of the impacts of heterospecific pollen upon plant reproduction

### 2019-03-15 Manuscript_draft/Tables_and_figures.Rmd
text edits and plot of total pollen to tables and figures

>>>>

\newpage
```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE,fig.height=8,fig.width=5}
load("Data/total_pollen.RData")
library(ggpubr)
library(ggplot2)
library(gridExtra)
library(grid)

p1 <- ggplot(total_pollen_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="A) Brassicaceae") +
  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
  geom_hline(yintercept = 50) + xlab("") + ylab("Total pollen")

p2 <- ggplot(total_pollen_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="B) Solanaceae") +
  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
  geom_hline(yintercept = 50) + xlab("") + ylab("Total pollen")

p3 <-ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="C) Convolvulaceae") +
  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
  geom_hline(yintercept = 50) + xlab("") + ylab("Total pollen")
grid.arrange(p1, p2,p3, nrow = 3, ncol=1)

```
**Figure 9**
